---
title: "mia 2 - results"
author: "shawn schwartz"
date: "`r tolower(format(Sys.time(), '%A %B %d, %Y @ %X'))`"
output: 
  html_document:
    highlight: tango
    theme: cosmo
    df_print: paged
    toc: true
    toc_float: 
      collapsed: false
    toc_depth: 4
    number_sections: true
---

# stroop task

## load libs
```{r warning=FALSE, message=FALSE}
library("tidyverse")
```

## plot settings
```{r}
txt <- element_text(size = 30, family = "Avenir", color = "black")

theme_set(
  theme_classic() +
    theme(legend.position = "none",
          text = txt,
          axis.text = txt)
)
```

## load raw data
```{r warning=FALSE, message=FALSE}
path.data <- file.path("~", "Downloads", "mia2_submissions.csv")

df.stroop <- path.data %>% 
  read_csv(show_col_types = FALSE) %>% 
  separate("Timestamp", into = c("date", "time"), sep = " ") %>% 
  mutate(date = mdy(date), year = year(date)) %>% 
  filter(year == 2024) %>% 
  select(-date, -time) %>% 
  unique() %>% 
  rename(congruent = `Task 1: Copy & paste the amount of time (secs) elapsed it took you to complete \"The easy practice test\"`,
         incongruent = `Task 2: Copy & paste the amount of time (secs) elapsed it took you to complete \"The real hard test\"`,
         email = `Email Address`) %>% 
  mutate(ln_congruent = log(congruent),
         ln_incongruent = log(incongruent))
```

### independently detect outliers in each condition and remove all their data
```{r}
vec.congruent_outliers <- df.stroop %>% 
  rstatix::identify_outliers(congruent) %>% 
  pull(Name)

vec.incongruent_outliers <- df.stroop %>% 
  rstatix::identify_outliers(incongruent) %>% 
  pull(Name)

vec.outlier_ids <- c(vec.congruent_outliers, vec.incongruent_outliers)

df.stroop <- df.stroop %>% 
  filter(!Name %in% vec.outlier_ids)
```

* There were `r length(vec.congruent_outliers)` outliers identified in the congruent RTs.
* There were `r length(vec.incongruent_outliers)` outliers identified in the incongruent RTs.

## stroop task results (*N =* `r df.stroop %>% pull(email) %>% unique %>% length`)

### rt
```{r fig.width=8, fig.height=8, warning=FALSE}
set.seed(100)

df.stroop %>% 
  select(Name, ln_congruent, ln_incongruent) %>% 
  pivot_longer(cols = starts_with("ln_"),
               names_to = "condition",
               names_prefix = "ln_",
               values_to = "rt") %>% 
  ggplot(mapping = aes(x = condition,
                       y = rt,
                       color = condition)) +
  geom_jitter(width = 0.15,
              height = 0,
              alpha = 0.3,
              size = 6.5) +
  stat_summary(geom = "linerange", 
               fun.data = mean_cl_boot, 
               linewidth = 2,
               col = "black") +
  stat_summary(fun = mean,
               size = 1,
               col = "black") +
  labs(title = "Stroop Task",
       subtitle = paste0("Psych 45 - Spring 2024 (N = ", df.stroop %>% pull(email) %>% unique %>% length, ")"),
       x = "",
       y = "ln(RT)") +
  scale_color_brewer(palette = "Set1")
```
