---
title: "mia 5 - results"
author: "shawn schwartz"
date: "`r tolower(format(Sys.time(), '%A %B %d, %Y @ %X'))`"
output: 
  html_document:
    highlight: tango
    theme: cosmo
    df_print: paged
    toc: true
    toc_float: 
      collapsed: false
    toc_depth: 4
    number_sections: true
---

# emotion and memory

## load libs
```{r warning=FALSE, message=FALSE}
library("tidyverse")
```

## plot settings
```{r}
txt <- element_text(size = 18, family = "Avenir", color = "black")
txt.x.rot <- element_text(size = 14, family = "Avenir", color = "black", angle = 45, vjust = 0.5)
txt.y.rot <- element_text(size = 14, family = "Avenir", color = "black", angle = 0)

theme_set(
  theme_classic() +
    theme(legend.position = "none",
          text = txt,
          axis.text.x = txt.x.rot,
          axis.text.y = txt.y.rot)
)
```

## load raw data and parse response vectors
```{r warning=FALSE, message=FALSE}
longify = function(data){
  words <- unlist(
    strsplit(
      gsub("\"|\\[|\\]| |\n", "", as.character(data$Words)), 
      ",")
    )
  
  responses <- unlist(
    strsplit(
      gsub("\"|\\[|\\]| |\n", "", as.character(data$Responses)), 
      ",")
  )
  
  if (length(words) == length(responses)) {
    out <- data.frame(word = words, response = responses)
  } else {
    warning <- paste("warning: longify failes for subject", unique(data$Name))
    out <- data.frame(word = warning, response = NA)
  }
  
   return(out)
}
df.valence_ratings <- read_csv("valence_ratings.csv",
                               show_col_types = FALSE) %>% 
  mutate(word = as.character(word))

path.data <- file.path("~", "Downloads", "mia5_submissions.csv")

df.emo <- path.data %>% 
  read_csv(show_col_types = FALSE) %>% 
  distinct(Name, .keep_all = TRUE) %>% 
  group_by(Name) %>% 
  do(longify(.)) %>% 
  drop_na() %>% 
  left_join(df.valence_ratings, by = "word") %>% 
  mutate(response = as.numeric(response)) %>% 
  filter(!is.na(valence))
```

## valence

> proportion words recalled as a function of valence?

```{r fig.width=7, fig.height=7, warning=FALSE}
set.seed(100)

df.emo %>% 
  ggplot(mapping = aes(x = valence,
                       y = response,
                       color = valence)) +
  stat_summary(fun.data = "mean_cl_boot",
               fill = "black",
               size = 1) +
  scale_color_manual(values = c(
    "negative" = "red", 
    "neutral" = "blue",
    "positive" = "green")
  ) +
  labs(title = "Valence and Memory",
       subtitle = paste0("Psych 45 - Spring 2024 (N = ", df.emo %>% pull(Name) %>% unique %>% length, ")"),
       x = "valence",
       y = "proportion remembered") +
  coord_cartesian(ylim = c(0, 0.5))
```

> positive/negative words (i.e., more valenced words) are better remembered than the neutral words.

> exemplars of best remembered words:

```{r}
df.emo %>% 
  group_by(word) %>% 
  summarise(prop_recall = sum(as.numeric(response))/n()) %>% 
  arrange(-prop_recall) %>% 
  head(15) %>% 
  DT::datatable()
```

## presentation order (i.e., primacy/recency effect)
```{r}
df.serial <- df.emo %>% 
  group_by(Name) %>% 
  mutate(serial_pos = 1:n()) %>% 
  mutate(serial_cat = ifelse(serial_pos < 6, "primacy",
                             ifelse(serial_pos > 40, "recency",
                                    "middle of list"))) %>% 
  mutate(serial_cat = factor(serial_cat,
                             levels = c("primacy", "middle of list", "recency"))) %>%
  ungroup()

df.serial %>% 
  group_by(serial_cat) %>% 
  ggplot(mapping = aes(x = serial_cat,
                       y = response)) +
  stat_summary(fun.data = "mean_cl_boot",
               fill = "black",
               size = 1) +
  labs(title = "Serial Position Effect",
       subtitle = paste0("Psych 45 - Spring 2024 (N = ", df.emo %>% pull(Name) %>% unique %>% length, ")"),
       x = "list position",
       y = "proportion remembered") +
  coord_cartesian(ylim = c(0.3, 0.6))
  
df.serial %>% 
  group_by(serial_pos) %>% 
  ggplot(mapping = aes(x = serial_pos,
                       y = response)) +
  stat_summary(fun.data = "mean_cl_boot",
               fill = "black",
               size = 1) +
  geom_smooth() +
  labs(title = "Serial Position Effect",
       subtitle = paste0("Psych 45 - Spring 2024 (N = ", df.emo %>% pull(Name) %>% unique %>% length, ")"),
       x = "list position",
       y = "proportion remembered") +
  coord_cartesian(ylim = c(0, 0.75))
```

## valence + presentation order (i.e., primacy/recency effect)
```{r}
df.serial %>% 
  group_by(serial_cat, valence) %>% 
  ggplot(mapping = aes(x = serial_cat,
                       y = response,
                       group = valence,
                       color = valence)) +
  stat_summary(fun.data = "mean_cl_boot",
               position = position_dodge(.2),
               fill = "black",
               size = 1) +
  scale_color_manual(values = c("red", "green", "blue"))+
  labs(title = "Valence x Serial Position Effect",
       subtitle = paste0("Psych 45 - Spring 2024 (N = ", df.emo %>% pull(Name) %>% unique %>% length, ")"),
       x = "list position",
       y = "proportion remembered") +
  coord_cartesian(ylim = c(0.2, 0.75)) +
  theme(legend.position = "right")
  
df.serial %>% 
  group_by(serial_pos, valence) %>% 
  ggplot(mapping = aes(x = serial_pos,
                       y = response,
                       group = valence, 
                       col = valence)) +
  stat_summary(fun.data = "mean_cl_boot",
               geom="point",
               fill = "black",
               size = 1) +
  geom_smooth(alpha = 0.5, method = "loess") +
  labs(title = "Serial Position Effect",
       subtitle = paste0("Psych 45 - Spring 2024 (N = ", df.emo %>% pull(Name) %>% unique %>% length, ")"),
       x = "list position",
       y = "proportion remembered") +
  coord_cartesian(ylim = c(0.15, 0.75)) +
  theme(legend.position = "right")
```